---
title: "Investigation of exponential distribution"
author: "Andrey Alferov"
date: "Sunday, April 26, 2015"
output:
  pdf_document: default
---

This report provides the results of investigation of the properties of the distribution of the mean of 40 exponentials.
It contains:

1. comparison of the sample mean to the theoretical mean of the distribution;
2. variability of the sample (via variance) and its comparison to the theoretical variance of the distribution;
3. confirmation that the distribution is approximately normal.

```{r, warning=FALSE, message=FALSE}
library(ggplot2)

set.seed(1234)
```

####Sample Mean versus Theoretical Mean

Calculate the sample mean of 1000 averages of 40 exponentials.
```{r}
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(40,0.2)))
sample_mean <- mean(mns)
sample_mean
```

Calculate the theoretical mean (1/lambda)
```{r}
theoretical_mean <- 1 / 0.2 
theoretical_mean
```

Calculate the difference between the sample mean and the theoretical mean.
```{r}
results <- sample_mean - theoretical_mean
results
```

The results shows that the difference between the sample mean of large collection of averages of a number of randoms and the theoretical mean is very low. What prooves the Law of Large Numbers.

####Sample Variance versus Theoretical Variance

Calculate the variance of the distribution of 1000 averages of 40 random exponentials.
```{r}
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(40,0.2)))
sample_var <- var(mns)
sample_var
```

Calculate the theoretical variance ((1/lambda)^2/n)
```{r}
theoretical_var <- (1/0.2)^2/40
theoretical_var
```

Calculate the difference between the sample variance and the theoretical variance.
```{r}
results <- sample_var - theoretical_var
results
```

The results shows that the difference between the sample variance of large collection of averages of a number of randoms and the theoretical variance is very low. What prooves the Law of Large Numbers.

####Distribution

Plot the distribution of averages of 40 random exponentials and approximate it to the normal distirbution.
```{r, warning=FALSE, message=FALSE}
plot <- ggplot(data.frame(mns), aes(x = mns))
plot <- plot + geom_histogram(aes(y=..density..), color = "black", fill = "green")
plot + geom_density(colour="blue", size=1);
```
The plot above shows that the distribution fits the bell curve pretty well and thus is approximately normal.
